TBD

### 2021-03-11 outputs/paper/paper.Rmd
1234

Dummy_data<- fastDummies::dummy_cols(FS, remove_first_dummy = TRUE, remove_selected_columns = TRUE)%>%
  select(-c(4))#  change categorical var to factors

##create model
model <- lm(post_favor_Warren ~., data =Dummy_data )
summary(model)

>>>>

#Dummy_data<- fastDummies::dummy_cols(FS, remove_first_dummy = TRUE, #remove_selected_columns = TRUE)%>%
#  select(-c(4))#  change categorical var to factors

##create model
model <- lm(post_favor_Warren ~., data =FS )
summary(model)
